Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Distance

### 2019-01-21 ICML2019/main.tex
add algorithms

\subsubsection{A first approach: the $\expmech$ mechanism}
$\expmech(x,u,\candidateset)$  outputs an element $r\in\candidateset$ with  probability: % proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$.
\[
%\underset{z \thicksim \expmech(x,u,\candidateset) }{\Pr}[z=r] = \frac
\frac
  {\exp(\frac{\epsilon\cdot u(x,r)}{2 GS})}
{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{2\cdot GS})},
\]
where $u(x,r)$ is the Hellinger scoring function: $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity of the scoring function, defined as:
\begin{equation*}
GS \equiv 
\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}}\max_{\{r\in \mathcal{R}\}}
|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
\end{equation*}
%
  \begin{algorithm}
  \caption{$\expmech$ in Beta-binomial model}
  \label{mech:expmech}
  \begin{algorithmic}
  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, inference algorithm: $\bysinfer$, 
  prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$.  
  \STATE \quad {\bf Initialize} a vector $Pr = (0, \dots, 0 )$ of $|\candidateset|$ length.
  \STATE \quad {\bf For} $r$ in $\candidateset$:
  \STATE \quad \quad calculate the outputting probability of $r$.
  \STATE \quad \quad $Pr[r] = 
  {\exp(\frac{\epsilon\cdot u(x,r)}{2 GS})}
/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{2\cdot GS})}$
\STATE \quad sample $z$ from $\candidateset$ by probability distribution $Pr$.
  \STATE {\bf return} $z$
  \end{algorithmic}
  \end{algorithm}

@@

  \begin{algorithm}
  \caption{$\lexpmech$ in Beta-binomial model}
  \label{mech:expmech}
  \begin{algorithmic}
  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, inference algorithm: $\bysinfer$, 
  prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$.  
  \STATE \quad {\bf Initialize} a vector $Pr = (0, \dots, 0 )$ of $|\candidateset|$ length.
  \STATE \quad {\bf For} $r$ in $\candidateset$:
  \STATE \quad \quad calculate the outputting probability of $r$.
  \STATE \quad \quad $Pr[r] = 
  {\exp(\frac{\epsilon\cdot u(x,r)}{2 GS})}
/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{2\cdot GS})}$
\STATE \quad sample $z$ from $\candidateset$ by probability distribution $Pr$.
  \STATE {\bf return} $z$
  \end{algorithmic}
  \end{algorithm}

@@

\begin{thm}
  \label{thm_gamma_smooth}
  For any $\dataobs, \dataobs'\in\{0,1\}^n$, and $\gamma \in \mathbb{R}^{+}$
  if  $\adj{\dataobs}{\dataobs'}$ then $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$.
\end{thm}
The interested reader will find the proof in Appendix \ref{??}.
We are now ready to define the mechanism $\hexpmech$. $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
\[
  \frac {\exp\big(\frac{-\epsilon\cdot \ux{r}}{4\cdot S(\dataobs)}\big)}
  {\displaystyle\sum_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{4\cdot S(\dataobs)})},
\]
where $S(\dataobs)$ is the 1-smooth sensitivity of  $\hellinger(\bysinfer(\dataobs),\cdot)$. {\color{red}{why do we choose 1???}}
  \begin{algorithm}
  \caption{$\hexpmech$ in Beta-binomial model}
  \label{mech:expmech}
  \begin{algorithmic}
  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, inference algorithm: $\bysinfer$, 
  prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$.  
  \STATE \quad {\bf Initialize} a vector $Pr = (0, \dots, 0 )$ of $|\candidateset|$ length.
  \STATE \quad {\bf For} $r$ in $\candidateset$:
  \STATE \quad \quad calculate the outputting probability of $r$.
  \STATE \quad \quad $Pr[r] = 
  {\exp(\frac{\epsilon\cdot u(x,r)}{2 GS})}
/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{2\cdot GS})}$
\STATE \quad sample $z$ from $\candidateset$ by probability distribution $Pr$.
  \STATE {\bf return} $z$
  \end{algorithmic}
  \end{algorithm}

>>>>

\subsubsection{A first approach: the $\expmech$ mechanism}
$\expmech(x,u,\candidateset)$  outputs an element $r\in\candidateset$ with  probability: % proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$.
\[
%\underset{z \thicksim \expmech(x,u,\candidateset) }{\Pr}[z=r] = \frac
\frac
  {\exp(\frac{\epsilon\cdot u(x,r)}{2 GS})}
{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{2\cdot GS})},
\]
where $u(x,r)$ is the Hellinger scoring function: $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity of the scoring function, defined as:
\begin{equation*}
GS \equiv 
\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}}\max_{\{r\in \mathcal{R}\}}
|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
\end{equation*}
%
  \begin{algorithm}
  \caption{$\expmech$ in Beta-binomial model}
  \label{mech:expmech}
  \begin{algorithmic}
  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, inference algorithm: $\bysinfer$, 
  prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$. $GS$ be the global sensitivity of scoring function.  
  \STATE \quad {\bf Initialize} a vector $Pr = (0, \dots, 0 )$ of $|\candidateset|$ length.
  \STATE \quad {\bf For} $r$ in $\candidateset$:
  \STATE \quad \quad calculate the outputting probability of $r$.
  \STATE \quad \quad $Pr[r] = 
  {\exp(\frac{\epsilon\cdot u(x,r)}{2 GS})}
/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{2\cdot GS})}$
\STATE \quad sample $z$ from $\candidateset$ by probability distribution $Pr$.
  \STATE {\bf return} $z$
  \end{algorithmic}
  \end{algorithm}

@@

  \begin{algorithm}
  \caption{$\lexpmech$ in Beta-binomial model}
  \label{mech:expmech}
  \begin{algorithmic}
  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, inference algorithm: $\bysinfer$, 
  prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$. $LS$ be the local sensitivity of scoring function.  
  \STATE \quad {\bf Initialize} a vector $Pr = (0, \dots, 0 )$ of $|\candidateset|$ length.
  \STATE \quad {\bf For} $r$ in $\candidateset$:
  \STATE \quad \quad calculate the outputting probability of $r$.
  \STATE \quad \quad $Pr[r] = 
  {\exp(\frac{\epsilon\cdot u(x,r)}{2 LS})}
/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{2\cdot LS})}$
\STATE \quad sample $z$ from $\candidateset$ by probability distribution $Pr$.
  \STATE {\bf return} $z$
  \end{algorithmic}
  \end{algorithm}

@@

\begin{thm}
  \label{thm_gamma_smooth}
  For any $\dataobs, \dataobs'\in\{0,1\}^n$, and $\gamma \in \mathbb{R}^{+}$
  if  $\adj{\dataobs}{\dataobs'}$ then $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$.
\end{thm}
The interested reader will find the proof in Appendix.
We are now ready to define the mechanism $\hexpmech$. $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
\[
  \frac {\exp\big(\frac{-\epsilon\cdot \ux{r}}{4\cdot S(\dataobs)}\big)}
  {\displaystyle\sum_{r' \in \mathcal{R}}\exp(\frac{\epsilon\cdot u(x,r')}{4\cdot S(\dataobs)})},
\]
where $S(\dataobs)$ is the 1-smooth sensitivity of  $\hellinger(\bysinfer(\dataobs),\cdot)$. {\color{red}{why do we choose 1???}}
  \begin{algorithm}
  \caption{$\hexpmech$ in Beta-binomial model}
  \label{mech:expmech}
  \begin{algorithmic}
  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, inference algorithm: $\bysinfer$, 
  prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$. $S(\dataobs)$ be the vector of $\gamma-$sensitivity of scoring function. 
  \STATE \quad {\bf Initialize} a vector $Pr = (0, \dots, 0 )$ of $|\candidateset|$ length.
  \STATE \quad {\bf For} $r$ in $\candidateset$:
  \STATE \quad \quad calculate the outputting probability of $r$.
  \STATE \quad \quad $Pr[r] = 
  {\exp(\frac{\epsilon \cdot \ux{r}}{2 S(\dataobs)})}
/ {\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon \cdot}{2\cdot S(\dataobs)})}$
\STATE \quad sample $z$ from $\candidateset$ by probability distribution $Pr$.
  \STATE {\bf return} $z$
  \end{algorithmic}
  \end{algorithm}
